---
title: "Unconscious EC RRR"
subtitle: "Generate randomised trial order files"
author: "Ian Hussey^[Ghent University. Email: ian.hussey@ugent.be]"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    number_sections: no
    theme: flatly
    toc: yes
    toc_float: yes
---

# to do & notes

what counterbalancing options are necessary, e.g., 1) CS1-pos vs CS2-pos, and 2) 

should i make different files, one (or more) for each participant, or just one stimulus file and subset it by participant?

nb if it turns out that the csv files should be kept seperate instead to be used with different loops, they could be renamed using shuffle-popped names. 

generate 150 participants worth of data, but produce either one file per condition for each participant, or make all conditions for all participants and then subset this in the task randomly. e.g., so that each participant is randomly assigned to a condition.


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE, 
                      warning = FALSE)

# options
options(knitr.table.format = "html") # necessary configuration of tables

# disable scientific notation
options(scipen = 999) 

```

```{r}

# dependencies
check_for_and_install_packages <- function(package) {
  if (!package %in% installed.packages()) install.packages(package)
}

check_for_and_install_packages("tidyverse")

library(tidyverse)

```

# Generate trial sequence for learning phase

```{r}

# build vectors of CS US trials, randomise order
# these are popped from for all the 5 blocks so that they are never presented twice
n_CS_US_trials_per_block <- 20
trials_CS1_USpos <- paste(rep("CS1_USpos", n_CS_US_trials_per_block), seq(from = 1, to = n_CS_US_trials_per_block, by = 1), sep = "_")
trials_CS2_USneg <- paste(rep("CS2_USneg", n_CS_US_trials_per_block), seq(from = 1, to = n_CS_US_trials_per_block, by = 1), sep = "_")

# build vector of filler and target trials, randomise order
generate_block <- function(target_name, n_filler_trials_per_block = 52, n_target_trials_per_block = 10) {
  
  trials_filler <- paste(rep("filler", n_filler_trials_per_block), seq(from = 1, to = n_filler_trials_per_block, by = 1), sep = "_")
  trials_target <- paste(rep(target_name, n_target_trials_per_block), seq(from = 1, to = n_target_trials_per_block, by = 1), sep = "_")
  trials_combined <- append(trials_filler, trials_target) %>% sample()
  
  # insert CS-US trials into specific locations in a master vector
  popped_trial <- c("blank", sample(trials_CS1_USpos, 1), "blank")
  trials_CS1_USpos_shuffled <- trials_CS1_USpos[trials_CS1_USpos != popped_trial]
  trials_combined <- append(trials_combined, popped_trial, after = 9)
  
  popped_trial <- c("blank", sample(trials_CS2_USneg, 1), "blank")
  trials_CS2_USneg_shuffled <- trials_CS2_USneg[trials_CS2_USneg != popped_trial]
  trials_combined <- append(trials_combined, popped_trial, after = 19)
  
  popped_trial <- c("blank", sample(trials_CS1_USpos, 1), "blank")
  trials_CS1_USpos_shuffled <- trials_CS1_USpos[trials_CS1_USpos != popped_trial]
  trials_combined <- append(trials_combined, popped_trial, after = 29)
  
  popped_trial <- c("blank", sample(trials_CS2_USneg, 1), "blank")
  trials_CS2_USneg_shuffled <- trials_CS2_USneg[trials_CS2_USneg != popped_trial]
  trials_combined <- append(trials_combined, popped_trial, after = 39)
  
  popped_trial <- c("blank", sample(trials_CS1_USpos, 1), "blank")
  trials_CS1_USpos_shuffled <- trials_CS1_USpos[trials_CS1_USpos != popped_trial]
  trials_combined <- append(trials_combined, popped_trial, after = 49)
  
  popped_trial <- c("blank", sample(trials_CS2_USneg, 1), "blank")
  trials_CS2_USneg_shuffled <- trials_CS2_USneg[trials_CS2_USneg != popped_trial]
  trials_combined <- append(trials_combined, popped_trial, after = 59)
  
  popped_trial <- c("blank", sample(trials_CS1_USpos, 1), "blank")
  trials_CS1_USpos_shuffled <- trials_CS1_USpos[trials_CS1_USpos != popped_trial]
  trials_combined <- append(trials_combined, popped_trial, after = 69)
  
  popped_trial <- c("blank", sample(trials_CS2_USneg, 1), "blank")
  trials_CS2_USneg_shuffled <- trials_CS2_USneg[trials_CS2_USneg != popped_trial]
  trials_combined <- append(trials_combined, popped_trial, after = 79)
  
  return(trials_combined)
}


# create data for many participants
n_participants <- 150

trials <- NULL

for(i in 1:n_participants) {
  block_a <- generate_block(target_name = "target_a")
  block_b <- generate_block(target_name = "target_b")
  block_c <- generate_block(target_name = "target_c")
  block_d <- generate_block(target_name = "target_d")
  block_e <- generate_block(target_name = "target_e")
  
  blocks_combined <- block_a %>%
    append(., block_b, after = sample(c(0, 86), 1)) %>%
    append(., block_c, after = sample(c(0, 86, 86*2), 1)) %>%
    append(., block_d, after = sample(c(0, 86, 86*2, 86*3), 1)) %>%
    append(., block_e, after = sample(c(0, 86, 86*2, 86*3, 86*4), 1))
  
  data_participant <- data.frame(stimulus = blocks_combined) %>%
    rownames_to_column(var = "trial_number") %>%
    mutate(participant = i,
           trial_number = as.numeric(as.character(trial_number)))
  
  trials <- bind_rows(trials, data_participant)
}

# tidy and add trial type info to ease analysis
trials <- trials %>% 
  select(participant, trial_number, stimulus) %>%
  mutate(trial_type = ifelse(grepl("filler", stimulus), "filler",
                             ifelse(grepl("blank", stimulus), "blank",
                                    ifelse(grepl("target", stimulus), "target",
                                           ifelse(grepl("CS", stimulus), "CSUS", NA)))),
         target_trial = ifelse(grepl("target", trial_type), TRUE, FALSE)) %>%
  rownames_to_column(var = "row_number") %>%
  mutate(row_number = as.numeric(as.character(row_number)))

# write to disk
write_csv(trials, "trials.csv")

```


# code to be translated into python/pandas and used to subset rows for each block

```{r}

subset_participant <- trials %>%
  filter(participant == current_participant_code &
         condition == sample(c(1,2,3,4), 1))

subset_block_1 <- subset_participant %>%
  filter(trial_number %in% 1*participant:86*participant)

subset_block_2 <- subset_participant %>%
  filter(trial_number %in% 1*participant*2:86*participant*2)

subset_block_3 <- subset_participant %>%
  filter(trial_number %in% 1*participant*3:86*participant*3)

subset_block_4 <- subset_participant %>%
  filter(trial_number %in% 1*participant*4:86*participant*4)

subset_block_5 <- subset_participant %>%
  filter(trial_number %in% 1*participant*5:86*participant*5)

```





